---
title: "Lab 3"
author: "Haoyu Yu"
format: html
editor: visual
embed-resources: true
---

# Question 1: Read in the data.

```{r}
download.file(
  "https://raw.githubusercontent.com/USCbiostats/data-science-data/master/02_met/met_all.gz",
  destfile = file.path("~", "Downloads", "met_all.gz"),
  method   = "libcurl",
  timeout  = 60
)
met <- data.table::fread(file.path("~", "Downloads", "met_all.gz"))
met <- as.data.frame(met)
```

# Question 2: Check the dimensions, headers, footers.

```{r}
dim(met)
head(met)
tail(met)
```

# Question 3: Take a look at the variables.

```{r}
str(met)
```

# Question 4: Take a closer look at the key variables.

```{r}
table(met$year)
table(met$day)
table(met$hour)
summary(met$temp)
summary(met$elev)
summary(met$wind.sp)
met[met$elev==9999.0, ] <- NA
summary(met$elev)
met <- met[met$temp > -40, ]
head(met[order(met$temp), ])
sum(is.na(met$wind.sp))
```

# Question 5: Check the data against an external data source.

I find that the lowest temp is -17.2, which occurs in (38.767, -104.3). This place is near Colorado Springs, whose lowest temp is 59 in August, 2019. So, this data is an error.

```{r}
met <- met[met$temp > -17, ]
head(met[order(met$temp), ])
```

# Question 6: Calculate summary statistics
```{r}
elev <- met[which(met$elev == max(met$elev, na.rm = TRUE)), ]
summary(elev)
cor(elev$temp, elev$wind.sp, use="complete")
cor(elev$temp, elev$hour, use="complete")
cor(elev$wind.sp, elev$day, use="complete")
cor(elev$wind.sp, elev$hour, use="complete")
cor(elev$temp, elev$day, use="complete")
```

# Question 7: Exploratory graphs
```{r}
hist(met$elev, 
     main="Histogram of Elevation", 
     col="lightblue", 
     border="black")

hist(met$temp, 
     main="Histogram of Temperature", 
     col="lightgreen", 
     border="black")

hist(met$wind.sp, 
     main="Histogram of Wind Speed", 
     col="lightcoral", 
     border="black")
library(leaflet)
leaflet(elev) %>%
  addProviderTiles('OpenStreetMap') %>% 
  addCircles(lat=~lat,lng=~lon, opacity=1, fillOpacity=1, radius=100)

library(lubridate)
elev$date <- with(elev, ymd_h(paste(year, month, day, hour, sep= ' ')))
summary(elev$date)
elev <- elev[order(elev$date), ]
head(elev)
plot(elev$date, elev$temp, type='l')
plot(elev$date, elev$wind.sp, type='l')


```

# Question 8: Ask questions
I want to know the temperature distribution at different elevation.
```{r}
boxplot(met$temp ~ met$elev, main="Temperature by Elevation")
```

